In this thesis, a new ansatz for defining the canonical form of isometric tensor product states in 2D was implemented. In Chapter \ref{chap:tensors_and_tensor_networks} an introduction to tensor networks, isometric tensor networks, Matrix Product States (MPS) and isometric Tensor Product States (isoTPS) was given. The new ansatz for defining the canonical form on isoTPS, which we call YB-isoTPS, was introduced in Chapter \ref{chap:isoTPS_alternative_canonical_form}. Several algorithms were discussed for moving the orthogonality hypersurface through the YB-isoTPS, which is done by performing so-called Yang-Baxter (YB) moves. It was found that a Riemannian disentangling procedure that minimizes the truncation error yields the lowest error for a single YB move. This was also found in previous works on MM-isoTPS \cite{cite:isometric_tensor_network_states_in_two_dimensions, cite:efficient_simulation_of_dynamics_in_two_dimensional_quantum_spin_systems}. Further, an approximate algorithm was introduced for computing the required gradients and Hessian-vector products of the cost functions, decreasing the computational cost from $\mathcal{O}(D^9)$ to $\mathcal{O}(D^8)$. A qualitative comparison of the different methods revealed that the approximate versions of the algorithms perform nearly as well as the exact versions, while being significantly faster. The introduced algorithms were then tested in Chapters \ref{chap:toric_code} and \ref{chap:TFI}. In Chapter \ref{chap:toric_code} it was shown that YB-isoTPS are able to represent the ground state of the Toric Code model, with the YB move being able to shift the orthogonality hypersurface without error up to numerical accuracy. In Chapter \ref{chap:TFI}, imaginary and real time evolution with the TEBD algorithm was used to find ground states and perform global quenches of the Transverse Field Ising model. It was found that YB-isoTPS are able to produce similar results to MM-isoTPS. The algorithms performing best in the ground state search were found to be the Riemannian optimization algorithms minimizing the Rényi entropy with $\alpha = 1/2$. In a large scale simulation of up to $N = 800$ spins, numerical evidence was found that YB-isoTPS are able to correctly capture the area law entanglement structure of the ground state. While at this regime a reference simulation of DMRG on MPS with a large bond dimension of $\chi = 1024$ was still able to produce lower ground state energies, it is expected that this will change when moving to larger system sizes or more challenging models. Additionally, the ansatz was used to compute the ground state energy of the TFI model on a honeycomb lattice, showcasing that YB-isoTPS can be easily generalized to other lattice types. Computing a real time evolution after a global quench was found to be a very challenging problem for YB-isoTPS. Because of the accumulation of YB errors, the time evolution diverges from the reference simulation after short times. This issue becomes less significant when moving away from the critical point, which corresponds to an easier problem due to the slower growth of entanglement over time. Nevertheless, YB-isoTPS were found to be able to correctly capture short-time behaviour of two-dimensional lattice systems of $N = 128$ spins even at criticality. \par
To summarize, the YB-isoTPS ansatz is able to produce comparable results to MM-isoTPS. While the computational complexity of shifting the orthogonality hypersurface of YB-isoTPS is larger ($\mathcal{O}(D^8)$ compared to $\mathcal{O}(D^7)$) it is still an interesting alternative way of defining the isometry condition. One advantage of YB-isoTPS is the ease with which the ansatz can be generalized to different lattices. For instance, extending it to the Kagome lattice is expected to be feasible without increasing the cost of the YB move. Moreover, more involved algorithms like DMRG require the contraction of a boundary MPS, which has a computational complexity scaling as $\mathcal{O}(D^{12})$. For such algorithms, we expect the increased cost for the YB move compared to the MM to not make a large difference. \par
It would be interesting to implement a DMRG algorithm on YB-isoTPS and compare its performance to isoTPS. Future research could explore alternative algorithms for performing the YB move, which we find to be the main source of errors. Similar to MM-isoTPS, implementing a variational optimization on the complete column when shifting the orthogonality surface may be beneficial, as this was found to be essential for achieving good results when performing time evolution with MM-isoTPS \cite{cite:efficient_simulation_of_dynamics_in_two_dimensional_quantum_spin_systems}. Additionally, extending the method to the thermodynamic limit and further investigating the connection between isoTPS and quantum computing \cite{cite:topological_quantum_phase_transitions_in_2D_isometric_tensor_networks, cite:quantum_circuits_for_2D_isometric_tensor_networks} are promising research directions. Finally, the algorithm could significantly benefit from an implementation on Graphics Processing Units (GPUs), which can greatly accelerate tensor contractions and decompositions while also increasing the power efficiency.