We compute the ground state of the TFI model \eqref{eq:TFI_Hamiltonian} using disoTPS and TEBD with imaginary time $\tau = -i t$. As initial state we choose the product state $|\Psi_i\rangle=|\uparrow\rangle\otimes\cdots\otimes|\uparrow\rangle$ of all spins pointing up. One can expand the initial state in terms of energy eigenstates
\begin{equation}
	|\Psi_i\rangle = \sum_{n} \Psi_n |n\rangle.
\end{equation}
Applying the time evolution and normalizing then leads to the state
\begin{equation}
	|\Psi(t)\rangle = e^{-i\tau\hat{H}} |\Psi_i\rangle = \frac{1}{\mathcal{N}} \sum_{n} \Psi_n e^{-iE_n\tau} |n\rangle = \frac{1}{\mathcal{N}} \sum_{n} \Psi_n e^{-E_nt} |n\rangle
\end{equation}
with
\begin{equation}
	\mathcal{N} = \left\lVert\sum_{n} \Psi_n e^{-E_nt}\right\rVert
\end{equation}
If we now take the limit $t \rightarrow \infty$ and assume that the ground state $|0\rangle$ with the lowest energy $E_0$ is nondegenerate, all states except the ground state vanish because of the exponential terms $e^{-E_nt}$. We end up with the ground state
\begin{equation}
	|\Psi(t\rightarrow\infty)\rangle = |0\rangle.
\end{equation}
To use the TEBD algorithm we must choose a good step size $\Delta t$. The total error of a single TEBD step evolving the disoTPS by (imaginary) time $\Delta t$ is a sum of three errors,
\begin{equation}
	\varepsilon_\text{TEBD} = \varepsilon_\text{Trotter} + \varepsilon_\text{trunc} + \varepsilon_{\text{YB}}.
\end{equation} 
The trotterization error $\varepsilon_\text{Trotter}$ comes from the Suzuki-Trotter decomposition, the truncation error $\varepsilon_\text{trunc}$ from locally applying the bond operators, and the YB error $\varepsilon_{\text{YB}}$ gets introduced when shifting the orthogonality hypersurface. A smaller time step $\Delta t$ decreases both $\varepsilon_\text{Trotter}$ and $\varepsilon_\text{trunc}$ while the YB error $\varepsilon_{\text{YB}}$ is not directly affected. However, since for a smaller time step $\Delta t$ more TEBD iterations are necessary to approach the limit $t\rightarrow\infty$, YB errors add up and prevent the state from reaching the true ground state. Therefore we expect, similar to \cite{cite:isometric_tensor_network_states_in_two_dimensions, cite:efficient_simulation_of_dynamics_in_two_dimensional_quantum_spin_systems}, that the YB-error dominates for small time steps, while the trotterization and truncation errors dominate for larger time steps. The best results can be achieved when the time step $\Delta t$ is tuned such that $\varepsilon_\text{Trotter} + \varepsilon_\text{trunc} \approx \varepsilon_{\text{YB}}$. \par
In figure \figref{} we benchmark the different algorithms for the YB move that were discussed in section \ref{sec:disoTPS_yang_baxter_move}. We perform an imaginary time evolution of the TFI model with a transverse field of $g = 3.5$, using second order TEBD and time steps $\Delta t \in \left[0.02, 0.5\right]$. The model is put on a $4\times4$ square lattice containing $32$ spins. For each data point we start at $\Delta t = 0.5$, slowly decreasing the time step until arriving at the desired time step $\Delta t$. We then perform another $50$ TEBD iterations and compute the average energy of the last 20 iterations. We then compute the relative error compared to the numerically exact DMRG reference simulation with a bond dimension of $\chi = 1024$ and plot the error against the time step $\Delta t$. \par
For figure \figref{}(a) we used a simple SVD for the YB move. The resulting error is large and the ground state energy is only found up to an accuracy of $10^{-3}$. If we use the initialization discussed in appendix \ref{} as a guess for the disentangling unitary, the ground state estimate improves by half an order of magnitude, see \figref{}(b). Using the Evenbly-Vidal algorithm for the YB move as discussed in section \ref{sec:YB_move_iterative_local_optimization} results in a comparable error, see \figref{}(c). In \figref{}(d) we used the Evenbly-Vidal algorithm for disentangling, optimizing the Rényi entropy with $\alpha = 2$. This improves the results drastically, pushing the relative error down to $10^{-5}$. Figures \figref{}(e)-(h) show the results when disentangling by optimizing the truncation error using Riemannian optimization. This performs slightly worse than when optimizing the Renyi-entropy. The reason for this is the following: While minimizing the truncation error leads to a better local YB-move it can lead to a larger error for the following YB-moves on the column. \todo{besser formulieren}. Conjugate Gradients (CG) and the Trust Region Method (TRM) perform similarly. Notably, the approximate version of both algorithms performs almost as good as the exact version while being much faster. Finally in figures \ref{}(i-l) we show the YB move with disentangling optimizing the Rényi entropy with $\alpha = 1/2$. Out of all methods tested this obtains the most accurate results. The TRM is able to achieve a slightly lower error than CG. We again observe that the approximate versions of both CG and TRM perform as well as the exact algorithms. \par
To conclude, we find that disentangling while optimizing the Rényi $\alpha=1/2$ entropy with the approximate TRM is the best method out of the methods tested. We will therefore use this method for the following plots. \par
\input{figures/plots/TFI/gs_energy_vs_dtau/gs_energy_vs_dtau_different_methods.tex}
It is also interesting to observe how many iterations of optimization are necessary for the disentangling to converge. In figure \figref{} we compare different values for the maximum number of iterations $N_\text{iters} = 50, 100, 200$. We observe that already for $N_\text{iters} = 50$ the algorithm is converged. \par
\input{figures/plots/TFI/gs_energy_vs_dtau/gs_energy_vs_dtau_different_N_iters.tex}
As discussed in section \ref{sec:disoTPS_TEBD} both first and second order TEBD require the same number of YB-moves, while second order TEBD leads to a smaller trotterization error $\varepsilon_\text{Trotter}$ and therefore allows us to go to larger time steps $\Delta t$. In figure \figref{} we compare TEBD of first and second order and observe the expected behaviour. The lowest energy is achieved at a smaller timestep compared to TEBD2, and the error of TEBD1 is a magnitude larger than that of TEBD2. \todo{Discuss that maybe the local truncation error increases?}\par
\input{figures/plots/TFI/gs_energy_vs_dtau/gs_energy_vs_dtau_TEBD1_vs_TEBD2.tex}
Next, we will go to larger system sizes. The ground state energy density obtained by imaginary TEBD is shown in figure \figref{}. The reference data was again computed using DMRG on MPS. We additionally extrapolated the MPS bond dimension $\chi\rightarrow\infty$ to obtain a better energy estimate. This extrapolation was performed by plotting the energy against the truncation error at different bond dimensions and extrapolating to a truncation error of zero. In the limit $L\rightarrow\infty$ we expect the energy density to approach a constant $E/N\rightarrow \text{const}$, whereas the energy density of small systems is dominated by finite size effect. We observe that the energy density computed using DMRG first gets lower but then rises again when increasing system size. This happens earlier for smaller bond dimensions and can be explained by the fact that the MPS is not able to correctly capture the entanglement structure of the model. In contrast, the energy density computed using disoTPS doesn't show this effect and seems to approach a constant energy density. This can be interpreted as the disoTPS being able to correctly capture area law entanglement. This effect is perhaps better visible in figure \figref{}, where we plot the relative ground state energy error compared to the extrapolated energy that was computed using DMRG $\chi\rightarrow\infty$. While for the system sizes we looked at DMRG is still able to find a state with a lower energy than disoTPS, we expect this to change for even larger systems or for more complicated models, where capturing the area law entanglement structure becomes more important. \par
\input{figures/plots/TFI/gs_search/gs_search_larger_systems.tex}
\input{figures/plots/TFI/gs_search/gs_search_larger_systems_log.tex}
Last, to show the generalization of disoTPS to other lattice types, we implemented disoTPS on the honeycomb lattice. The network structure is shown in figure \figref{}. For details of the implementation see \cite{}\todo{cite github}. For honeycomb disoTPS it can be beneficial to choose a larger bond dimension $D_\text{horizontal}$ for horizontal bonds, since else the maximal bond dimension of the diagonal bonds is not reached even in the bulk, see figure \figref{}. We test this in figure \figref{}, where we compute the ground state energy of the TFI model on a $4\times4$ honeycomb lattice. We run the algorithm once with $D_\text{horizontal} = D$ and once with $D_\text{horizontal} = D^2$. Unsurprisingly, increasing the bond dimension improves the results. Further testing should be done to study which bond dimension should be chosen in practice.
\input{figures/plots/TFI/gs_energy_vs_dtau/gs_energy_vs_dtau_honeycomb.tex}