As a second experiment, we study the capabilities of YB-isoTPS to perform real-time evolution. For this we perform a global quench by initializing the YB-isoTPS to a product state, which we then evolve in time, measuring local expectation values. We start with an all-up-state $\ket{\Psi} = \ket{\uparrow}\otimes\cdots\otimes\ket{\uparrow}$ on the $8\times8$ diagonal square lattice and evolve with the Hamiltonian of the TFI model at critical transverse field $g \approx 3.04438$. At the critical field the entanglement grows very quickly, making this a hard problem. For the YB-isoTPS we choose bond dimensions of $D\in\left\{2, 3, 4, 5, 6\right\}$, $\chi = 6\cdot D$ and a step size of $\Delta t = 0.02$. We evolve up to time $t = 1.0$, requiring 50 full TEBD iterations. For the YB-move we used approximate TRM disentangling optimizing the Rényi $\alpha = 0.5$ entropy for a maximum number of $N_\text{iter,YB} = 100$ iterations. For the application of the TEBD bond operators we used a maximum of $N_\text{iter,TEBD} = 100$ iterations. For a comparison we used the MPO-time evolution algorithm from \cite{cite:time_evolving_a_mps_with_long_range_interactions} defined on MPS, which is able to perform time evolution in the presence of long range interactions and is implemented in tenpy \cite{cite:tenpy}. For this reference simulation we used bond dimensions ranging from $\chi = 16$ to $\chi= 1024$ and a time step of $\Delta t = 0.01$. We show the results in Figure \figref{fig:YB_isoTPS_time_evolution_g_critical}. We observe that YB-isoTPS is in good agreement with the reference simulation up to a time of $t\approx0.2$, at which the expectation value diverges. This happens at earlier times for smaller bond dimensions $D$. We expect that this fast divergence is due to the accumulated error of the YB move. One could improve the method by applying a per-column variational optimization as done in isoTPS \cite{cite:isometric_tensor_network_states_in_two_dimensions, cite:efficient_simulation_of_dynamics_in_two_dimensional_quantum_spin_systems}, which was found to be essential for real-time evolution \cite{cite:efficient_simulation_of_dynamics_in_two_dimensional_quantum_spin_systems}, or by otherwise improving the YB move. \par
\input{figures/plots/TFI/global_quench/global_quench_g_critical.tex}
\input{figures/plots/TFI/global_quench/global_quench_g_6.tex}
Finally, we want to test the time evolution in a less challenging regime, for which we used the TFI model at a transverse field of $g = 6$, which is well in the paramagnetic phase. In this regime, entanglement is expected to build up much slower than when simulating at the critical field. We again initialize an all-up-state $\ket{\Psi} = \ket{\uparrow}\otimes\cdots\otimes\ket{\uparrow}$ on the $8\times8$ square lattice but additionally flip a spin in the center into the down-state $\ket{\downarrow}$. We then compute the time evolution of the $\langle\hat{\sigma}_z\rangle$ expectation value of the flipped center spin and neighboring spins. The results are shown in Figure \figref{fig:YB_isoTPS_time_evolution_g_6}. Note that the DMRG reference simulation converges for much lower bond dimensions $\chi$ compared to Figure \figref{fig:YB_isoTPS_time_evolution_g_critical}. We also observe much better agreement of YB-isoTPS TEBD and MPS DMRG.