\documentclass[encoding=utf8,british]{template/thesis}
\usepackage[OT1]{fontenc}
\usepackage[export]{adjustbox}
\usepackage{braket}
\usepackage{ragged2e}
\justifying

\pgfplotsset{compat=1.18}

%\usepgfplotslibrary{external}
%\tikzexternalize

\subject{Abschlussarbeit im Masterstudiengang Physik der Kondensierten Materie}
\title{Entwicklung eines diagonalen isometrischen Tensor Netzwerk Algorithmus}
\subtitle{Development of a Diagonal Isometric Tensor Network Algorithm}
\author{Benjamin Sappler}
\date{30.~Juli 2024}

\mathtoolsset{showonlyrefs}

\lowertitleback{Erstgutachter (Themensteller): Prof. Dr. Frank Pollmann\\
	Zweitgutachter:  Prof. Dr. Michael Knap}

\makeatletter
\renewcommand*\subcaption@label{%
	\caption@withoptargs\subcaption@@label}
\makeatother

% For aligning subfigures vertically
\newsavebox{\largestimage}
\newsavebox{\largestimagea}
\newsavebox{\largestimageb}
\newsavebox{\largestimagec}

\captionsetup[figure]{font=small}

% axis style, ticks, etc
\pgfplotsset{every axis/.append style={
		label style={font=\small},
		tick label style={font=\small}
}}

\begin{document}
	\frontmatter
	\maketitle
	
	\newpage
	\begin{refsection}
	\thispagestyle{empty}
	
	\null\vfill
	\raggedright\noindent
	I hereby declare that this thesis is entirely the result of my own work except where otherwise indicated. I have only used the resources given in the list of references. \par
	\vspace{2cm}
	\noindent
	\rlap{München, 30.~Juli 2024}{%
		\hspace{.5\textwidth}Benjamin Sappler}\par
	
	\newpage
	\thispagestyle{empty}
	
	\justifying
	
	\section*{Abstract}
	The numerical simulation of strongly interacting quantum many-body systems is a very challenging problem because of the exponential growth of the Hilbert space with system size. In the last decades, Tensor Networks have emerged as the standard method for tackling this problem in one dimensional systems in the form of Matrix Product States (MPS). Tensor Networks have also been generalized for the highly relevant problem of two and more spatial dimensions. However, these so-called Projected Entangled Pair States (PEPS) are typically plagued by high computational complexity and drastic approximations. Recently, a new class of Tensor Networks, called isometric Tensor Product States (isoTPS), has been introduced for the simulation of two-dimensional quantum systems. This new class of Tensor Networks generalizes the canonical form of Matrix Product States to higher dimensions. In this work, we develop an alternative way of defining this canonical form by rotating the lattice by 45$^\circ$ and introducing auxiliary tensors. This alternative ansatz is then tested by performing ground state search and real-time evolution of the Transverse Field Ising (TFI) model on large square lattices of up to 800 spins.
	
	\tableofcontents
	\thispagestyle{empty}
	
	\mainmatter
	
	\chapter{Introduction}
	\label{chap:introduction}
	\input{chapters/introduction/introduction.tex}
	
	\chapter{Tensors and Tensor Networks}
	\label{chap:tensors_and_tensor_networks}
	\input{chapters/Tensor_Networks/Tensor_Networks.tex}
	
	\chapter{IsoTPS with Alternative Canonical Form}
	\label{chap:isoTPS_alternative_canonical_form}
	\input{chapters/YB_isoTPS/YB_isoTPS.tex}
	
	\chapter{The Toric Code: An Exactly Representable Model}
	\label{chap:toric_code}
	\input{chapters/Toric_Code/Toric_Code.tex}
	
	\chapter{The Transverse Field Ising Model: Ground State Search and Time Evolution}
	\label{chap:TFI}
	\input{chapters/TFI/TFI.tex}
	
	\chapter{Conclusion and Outlook}
	\label{chap:summary}
	\input{chapters/conclusion_and_outlook/conclusion_and_outlook.tex}
	
	\appendix
	\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}% This turns off sections
	
	\chapter{Optimization Problems for Isometric Tensor Networks}
	\label{app:optimization_problems_for_isometric_tensor_networks}
	\input{chapters/optimization_problems_on_isometric_tensor_networks/optimization_problems_on_isometric_tensor_networks.tex}
	
	\chapter{Riemannian Optimization of Isometries}
	\label{app:riemannian_optimization_of_isometries}
	\input{chapters/Riemannian_Optimization/Riemannian_Optimization.tex}
	
	\chapter{Computing the Gradient and Hessian of the Disentangling Cost Functions}
	\label{app:computation_of_gradient_and_hvp_for_riemannian_optimization}
	\input{chapters/computation_of_gradient_and_hvp_for_riemannian_optimization/computation_of_gradient_and_hvp_for_riemannian_optimization.tex}	
	
	\backmatter
	\printbibliography
	\end{refsection}
	\begin{refsection}
	\nocite{Website:ColorBrewer}
	\nocite{Website:ColorBlind}
	\printbibliography[heading=subbibliography, title={Resources for Plotting}]
	\end{refsection}
	
\end{document}